---
output: github_document
---

```{r, message=FALSE, warning=FALSE, include=FALSE}
devtools::install_github("meirelesff/rscielo")
library(rscielo)
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-",
  ev = "png", 
  dev.args = list(type = "cairo"),
  dpi = 96
)
```

rscielo
=====

[![Travis-CI Build Status](https://travis-ci.org/meirelesff/rScielo.svg?branch=master)](https://travis-ci.org/meirelesff/rScielo) [![AppVeyor Build Status](https://ci.appveyor.com/api/projects/status/github/meirelesff/rScielo?branch=master&svg=true)](https://ci.appveyor.com/project/meirelesff/rScielo) [![Package-License](https://img.shields.io/badge/license-GPL%20%28%3E=%202%29-brightgreen.svg?style=flat)](http://www.gnu.org/licenses/gpl-2.0.html) [![CRAN_Status_Badge](http://www.r-pkg.org/badges/version/rscielo)](https://cran.r-project.org/package=rscielo)

`rscielo` provides functions to scrape data from scientific articles hosted on the [Scientific Electronic Library Online Platform (Scielo.br)](http://www.scielo.br/). The retrieved data includes authors' names and institutional affiliations, articles' contents and their meta-data, bibliographic references, among several others. The package also offers functions to summarize the scrapped data.


### How does it work?

#### Getting a journal's ID

The `rscielo` package scrapes data based on a journal ID (or pid). For example, this is the url of the Brazilian Political Science Review homepage on [Scielo](http://www.scielo.br/):

```
http://www.scielo.br/scielo.php?script=sci_serial&pid=1981-3821&lng=en&nrm=iso
```

The ID is located between `&pid=` and `&lng` (i.e., `1981-3821`). Most `rscielo`'s functions rely on this argument to extract data. To automatically extract an ID from a journal hosted on [Scielo](http://www.scielo.br/), you may use the convenient `get_journal_id()` function:

```{r, message=FALSE, warning=FALSE}
get_id_journal("http://www.scielo.br/scielo.php?script=sci_serial&pid=1981-3821&lng=en&nrm=iso")

```


#### Scraping data

To scrape meta-data from all articles of a journal hosted on [Scielo](http://www.scielo.br/), use the `get_journal()` function:

```{r, message=FALSE, warning=FALSE, results='hide'}
df <- get_journal("1981-3821")

```

Then summarize the scrapped data with `summary`:


```{r, echo=TRUE, message=FALSE, warning=FALSE}
summary(df)

```


The `rscielo` also contains a function to scrape meta-data from a single article:


```{r, eval=FALSE, message=FALSE, warning=FALSE}
# The article's URL on Scielo
url <- "http://www.scielo.br/scielo.php?script=sci_arttext&pid=S1981-38212016000200201&lng=en&nrm=iso&tlng=en"

# Scrape the data
article <- get_article(url)

```

Finally, `get_journal_info()` and `get_journal_list()` scrapes a journal's meta-information (publisher, ISSN, and mission) and a list of all journals hosted on [Scielo](http://www.scielo.br/), respectively:

```{r, eval=FALSE, message=FALSE, warning=FALSE}
# Get a journal's meta-information
meta_info <- get_journal_info("1981-3821")

# Get a list with all journals names, URLs and IDs
journals <- get_journal_list()

```


#### Scraping metrics

`rscielo`, it is possible to scrape several publication and citation metrics of a journal hosted on [Scielo](http://www.scielo.br/):

```{r, eval=FALSE, message=FALSE, warning=FALSE}
# Gets citation metrics
cit <- get_journal_metrics("1981-3821")

# Plots the data for a quick visualization
plot(cit)

```


### Functions

Here is a description of the `rScielo` functions:

* `get_id_journal()`: Gets a journal's ID from its url.
* `get_journal()`: Gets meta-data from all articles published by a journal.
* `get_article()`: Gets meta-data from a single article.
* `get_journal_info()`: Gets a journal's description.
* `get_journal_list()`: Gets a list with all journals' names, URLs and ID's.
* `get_journal_metrics()`: Gets publication and citation metrics of a journal.


### Installation

Install the latest stable release from [CRAN](http://cran.r-project.org/) via:

```{r, eval=FALSE, message=FALSE, warning=FALSE}
install.packages("rScielo")
```


Alternatively, install the latest pre-release version from [GitHub](https://github.com/) via:

```{r, eval=FALSE, message=FALSE, warning=FALSE}
if (!require("devtools")) install.packages("devtools")
devtools::install_github("meirelesff/rScielo")
```


### Author

[Fernando Meireles](http://www.fmeireles.com)
[Denisson Silva](http://www.denissonsilva.com)
Rogerio Barbosa

### License

GPL 3
